### 2021-04-07 Chapter-2/Chapter-2.tex
Updates from Overleaf

\section{Quantification}
Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward},
Quantitative Information Flow (QIF) aims at providing an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
of the information are leaked, the program is called non-interference. McCamant
and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
flow capacity. Backes et al.~\cite{5207642} propose an automated method for QIF
by computing an equivalence relation on the set of input keys. But the approach
cannot handle real-world programs with bitwise operations.
Phan et al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
work is to ensure a program is non-interference. They adopt an over
approximation method to estimate the total information leakage and their method
does not work for secret-dependent memory access side-channels.
Pasareanu et al.~\cite{pasareanu2016multi} combine symbolic analysis and Max-SMT solving to synthesize the concrete public input that can lead to the worst case leakage. They assume the target program has multiple different input secrets and calculate the average leakage for one-fixed public input.
CHALICE~\cite{Chattopadhyay:2017:QIL:3127041.3127044} quantifies the leaked
information for a given cache behavior.
It symbolically reasons about cache
behavior and estimates the amount of leaked information based on cache miss/hit.
Their approach only scale to small programs, which limits its usage in
real-world applications. On the contrary, \tool{} assesses the sensitive level
of side-channels with different granularities. It can also analyze side-channels
in real-world crypto libraries.

Model counting refers to the problem of computing the number of
models for a propositional formula (\#SAT). There are two approaches to
solving the problem, exact model counting and approximate model
counting. We focus on approximate model counting since it is our approach. Wei and Selman~\cite{wei2005new} introduce
ApproxCount, a local search based method using Markov Chain Monte
Carlo (MCMC). ApproxCount has the better scalability than
exact model counters. Other approximate model counter includes
SampleCount~\cite{gomes2007sampling},
Mbound~\cite{gomes2006model}, and MiniCount~\cite{kroc2008leveraging}.
Unlike ApproxCount,
these model counters can give lower or upper bounds with guarantees.
Despite the rapid development of model counters for SAT and some
research~\cite{chistikov2017approximate,phan2015model} on Modulo Theories model counting (\#SMT),
they cannot be directly applied to
side channel leakage quantification.
ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification,
but it has only been tested with small programs.

>>>>

\section{Quantification}
Proposed by Denning~\cite{robling1982cryptography} and Gray~\cite{gray1992toward},
Quantitative Information Flow (QIF) aims at providing an estimation of the amount of leaked information from the sensitive information given the public output. If zero bits
of the information are leaked, the program is called non-interference. 
McCamant and Ernst~\cite{McCamantE2008} quantify the information leakage as the network
flow capacity. They model the possible information leakage as a network of limited-capacity
channel. After that, they use the maximum rate of the channel to represent the amount of 
secret information that the execution can reveal.
Backes et al.~\cite{5207642} propose an automated method for QIF
by computing an equivalence relation on the set of input keys. However,
the evaluation shows the approach only works on small programs.
Besides, their approach cannot handle programs with bitwise operations.
However, such bitwise operations are quite common in cryptographic libraries.
Phan et al.~\cite{Phan:2012:SQI:2382756.2382791} propose symbolic QIF. The goal of their
work is to ensure a program is non-interference. They adopt an over
approximation method to estimate the total information leakage and their method
does not work for secret-dependent memory access side-channels.
Pasareanu et al.~\cite{pasareanu2016multi} combine symbolic analysis and Max-SMT solving to synthesize the concrete public input that can lead to the worst case leakage. They assume the target program has multiple different input secrets and calculate the average leakage for one-fixed public input.
CHALICE~\cite{Chattopadhyay:2017:QIL:3127041.3127044} quantifies the leaked
information for a given cache behavior.
It symbolically reasons about cache
behavior and estimates the amount of leaked information based on cache miss/hit.
Their approach only scale to small programs, which limits its usage in
real-world applications. On the contrary, \tool{} assesses the sensitive level
of side-channels with different granularities. It can also analyze side-channels
in real-world cryptographic libraries.

Model counting refers to the problem of computing the number of
solutions for a propositional formula (\#SAT). There are two approaches to
solving the problem, exact model counting and approximate model
counting. We focus on approximate model counting since it is our approach. Wei and Selman~\cite{wei2005new} introduce
ApproxCount, a local search based method using Markov Chain Monte
Carlo (MCMC). ApproxCount has the better scalability than
exact model counters. Other approximate model counter includes
SampleCount~\cite{gomes2007sampling},
Mbound~\cite{gomes2006model}, and MiniCount~\cite{kroc2008leveraging}.
Unlike ApproxCount, these model counters can give lower or upper bounds with guarantees.
Despite the rapid development of model counters for SAT and some
research~\cite{chistikov2017approximate,phan2015model} on Modulo Theories model counting (\#SMT), they cannot be directly applied to side channel leakage quantification.
ApproxFlow~\cite{biondi2018scalable} uses ApproxMC~\cite{chakraborty2016algorithmic} for information flow quantification, but it has only been tested with small programs.
